A Dependently Typed Multi-Stage Calculus

### 2019-08-25 text/related-work.tex
Add a description for Ur.

MetaOCaml is a programming language with quoting, unquoting, run, and
CSP.  Kiselyov~\cite{8384206} describes many applications of MetaOCaml, including filtering in signal processing, matrix-vector product,
and a DSL compiler.

@@

Although there are studies on combinations of multi-stage programming and
other programming features such as mutable cells~\cite{kiselyov2016refined} and
control operators~\cite{KameyamaKiselyovShan09PEPM,oishi2017staging}, a
combination with dependent types has been little studied. One exception is
Brady and Hammond~\cite{brady2006dependently}, who have discussed a
combination of dependently typed programming with staging in the style of
MetaOCaml to implement a staged interpreter, which is statically guaranteed
to generate well-typed code. However, they focused on concrete programming
examples and there is no theoretical investigation of the programming
language they used.

>>>>

% Practical research on multi-stage programming

MetaOCaml is a programming language with quoting, unquoting, run, and CSP.
Kiselyov~\cite{8384206} describes many applications of MetaOCaml, including
filtering in signal processing, matrix-vector product, and a DSL compiler.
Ur\cite{chlipala2010ur} is a programming language with metaprogramming, which
is focused on Web applications.

@@

Although there are studies on combinations of multi-stage programming and
other programming features such as mutable cells~\cite{kiselyov2016refined} and
control operators~\cite{KameyamaKiselyovShan09PEPM,oishi2017staging}, a
combination with dependent types has been little studied. One exception is
Brady and Hammond~\cite{brady2006dependently}, who have discussed a
combination of dependently typed programming with staging in the style of
MetaOCaml to implement a staged interpreter, which is statically guaranteed
to generate well-typed code. However, they focused on concrete programming
examples and there is no theoretical investigation of the programming
language they used. In order to make safer multi-stage programming language, 
Martin and Laurence~\cite{martin2015HGRTMP} gave program logic for
\(\text{Mini-ML}^\square_e\)~\cite{DaviesPfenning01JACM} but
it cannot manipulate open code which ours can deal with.
